ohun_paper_analyses

### 2022-07-13 README.Rmd
update readme

---
title: ohun_paper_analyses
author: Marcelo Araya Salas
output: github_document
date: `r format(Sys.Date(), "%d-%m-%Y")`
editor_options:
  chunk_output_type: console
---

>>>>

---
title: ohun_paper_analyses
author: "Marcelo Araya Salas"
output: github_document
editor_options:
  chunk_output_type: console
---
